%!TEX TS-program = pdflatex
%!TEX encoding = UTF-8 Unicode

% +++++++++++++++++++++++++++++++++++++++
% Curriculum Vitae
% Author: Simon Albrecht <simon@simonalbrecht.ch> 
%
% Based on AltaCV by LianTze Lim <liantze@gmail.com>.
%
% Licensed under BSD-3-Clause.
% Copyright (c) 2019, 2020, Simon Albrecht. 
% All rights reserved.
% +++++++++++++++++++++++++++++++++++++++
\documentclass[11pt, a4paper, ragged2e, withhyper]{altacv}

% ---------------------------------------
% Versioning
% ---------------------------------------
\newcommand{\version}{\input{VERSION}}

% ---------------------------------------
% Language, Spell Check, Encoding
% ---------------------------------------
\usepackage[british]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% ---------------------------------------
% Typography, Colors, Icons
% ---------------------------------------
\usepackage[sfdefault, light]{plex-sans}
\renewcommand*\familydefault{\sfdefault}

\usepackage{enumitem}
\usepackage[fixed]{fontawesome5}
\usepackage[autostyle=true,english=british]{csquotes}

% ---------------------------------------
% Layout
% ---------------------------------------
\usepackage{paracol}
\usepackage{geometry}
\geometry{
	% showframe,
	a4paper,
	top=1.25cm,
	bottom=1.25cm,
	left=1.25cm,
	right=1.25cm,
	nohead,
	nofoot
}

% Header & Footer
\usepackage{fancyhdr}
\fancypagestyle{default}{
	\fancyhf{}
	\renewcommand{\headrulewidth}{0pt}
	\renewcommand{\footrulewidth}{0pt}
	\rfoot{\vspace*{-\baselineskip}\textcolor{body}{\thepage}}
}

\fancypagestyle{last-page}{
  \fancyhf{}
  \renewcommand{\headrulewidth}{0pt}
  \renewcommand{\footrulewidth}{0pt}
  \cfoot{\vspace*{-\baselineskip}\textcolor{body}{Version \version}}
  \rfoot{\vspace*{-\baselineskip}\textcolor{body}{\thepage}}
}

% Use package for parallel columns instead of
% relying on AltaCV columns, which have weird
% behaviour when text breaks across page
\usepackage{paracol}

% ---------------------------------------
% Hyphenation
% ---------------------------------------
\hyphenation{DevOps}
\hyphenation{Avaloq}

% ---------------------------------------
% Misc
% ---------------------------------------
\pdfinfo{
   /Author (Simon Albrecht)
   /Title  (CV Simon Albrecht)
   /Subject (Curriculum Vitae)
   /Keywords (Curriculum Vitae;CV;Resume;Lebenslauf;Biography;Hiring;Job;LaTex)
}

% Fix issue with LaTeX error related to dead
% output cycles: https://github.com/Tufte-LaTeX/tufte-latex/issues/116
\maxdeadcycles=500

% ---------------------------------------
% AltaCV Customisation
% ---------------------------------------
\definecolor{DarkGrey}{HTML}{323232}
\definecolor{LightGrey}{HTML}{dadada}
\definecolor{Blue}{HTML}{007bff}

\colorlet{name}{DarkGrey}
\colorlet{tagline}{Blue}
\colorlet{heading}{DarkGrey}
\colorlet{headingrule}{LightGrey}
\colorlet{accent}{Blue}
\colorlet{body}{DarkGrey}
\colorlet{bullet}{Blue}

\renewcommand{\namefont}{\Huge\sffamily\bfseries}
\renewcommand{\taglinefont}{\Large\sffamily}
\renewcommand{\cvsectionfont}{\Large\sffamily\bfseries}
\renewcommand{\personalinfofont}{\small}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{$\bullet$}

% Info Fields
\NewInfoField{birthday}{\faAsterisk}
\NewInfoField{nationality}{\faFlag}
\NewInfoField{maritialstatus}{\faHeart}
\NewInfoField{locationAlt}{\faMapMarker*}

\renewcommand{\emailsymbol}{\faEnvelope}

% Custom Skill/Language Rating Marker
\renewcommand{\ratingmarker}{\faCircle}
\newcommand{\ratingemptymarker}{\faCircleO}

% Skill with normal/thin font instead of bold
\renewcommand{\cvskill}[2]{%
	\textcolor{emphasis}{#1}\hfill
	\foreach \x in {1,...,5}{%
	  \footnotesize\space{\ifnumgreater{\x}{#2}{\color{LightGrey}}{\color{bullet}}\ratingmarker}}\par%
	\smallskip
}

% CV Event with customised fonts and better display of time range and location
\renewcommand{\cvevent}[4]{%
  {\Large\color{emphasis}#1\par}
  \medskip\normalsize
  \ifstrequal{#2}{}{}{
  	{#2}}
  \ifstrequal{#3}{}{}{{
  	\hspace{0.5em}
  	{#3}}}
  \ifstrequal{#4}{}{}{{
  	\hspace{0.5em}
  	{#4}}}\par
  \medskip\normalsize
}

% Special CV Event for Education, Volunteering
\newcommand{\cveventbreak}[4]{%
  {\Large\color{emphasis}#1\par}
  \medskip\normalsize
  \ifstrequal{#2}{}{}{
  	{#2}}\par
  \ifstrequal{#3}{}{}{{
  	{#3}}}\par
  \ifstrequal{#4}{}{}{{
  	{#4}}}\par
  \medskip\normalsize
}

% Custom strength macro
\newcommand{\cvstrength}[2]{
	{\Large\color{emphasis}#1\par}
  \medskip\normalsize
  {#2}\par
}

% Solid rule divider
\renewcommand{\divider}{\textcolor{LightGrey}{\rule{\linewidth}{0.5pt}}\medskip}

% Section with thiner line and more spacing
\renewcommand{\cvsection}[2][]{%
  \bigskip%
  \ifstrequal{#1}{}{}{\marginpar{\vspace*{\dimexpr1pt-\baselineskip}\raggedright\input{#1}}}%
  {\color{heading}\cvsectionfont\MakeUppercase{#2}}\\%
  {\color{headingrule}\rule{\linewidth}{0.5pt}\par}\bigskip
}

% Personal info field without colored icon and smaller text
\RenewDocumentCommand{\printinfo}{m m o}{%
  \IfNoValueTF{#3}{%
    \mbox{{\small #1}~\utffriendlydetokenize{#2}\hspace{0.5em}}%
  }{%
      \mbox{{\small #1}~
      \href{#3}{\utffriendlydetokenize{#2}}\hspace{0.5em}}
  }%
}%

% +++++++++++++++++++++++++++++++++++++++
% Document
% +++++++++++++++++++++++++++++++++++++++

\begin{document}
	\name{Simon Albrecht}
	\tagline{Full-Stack Software Engineer}
	
	\personalinfo{
		\medskip
		
		\birthday{1994}
		\nationality{Swiss}
		\maritialstatus{Single}
		\locationAlt{Zurich, Switzerland}
	
		\medskip
		
		\phone{+41 79 685 30 63}
		\email{simon@simonalbrecht.ch}
		\linkedin{simonalbrecht}
		\github{simonalbrecht}
		\homepage{simonalbrecht.ch}
	}
\pagestyle{default}
\makecvheader

% Two column layout
\columnratio{0.65}
\setlength{\columnsep}{30pt}

\begin{paracol}{2}


	% ---------------------------------------
	% Experience
	% ---------------------------------------
	\cvsection{Experience}
	
	\cvevent{Senior Software Engineer}{\href{https://www.aiaibot.com/}{aiaibot (swiss moonshot AG)}}{Aug 2019 -- Dec 2020}{Zurich}

	\bigskip
	\begin{itemize}[label=\color{bullet}\textbullet]
		\item Senior Frontend Engineer, responsible for web development, software architecture, and user interface development of a Conversational AI / Chatbot SaaS platform.
		\item Developed the web-based realtime Chat Client that integrates easily and transparently into user web sites with a single line of code.
		\item Part of the core product team, worked closely with UI/UX Designers, Product Owners, and Software Engineers taking the product from idea to fully-featured platform.
		\item Carried out production releases, monitored operations and infrastructure, and automated DevOps processes.
	\end{itemize}

	\bigskip
	\begin{description}
		\small
		\item [Technologies:] Javascript (ES6), Vue.js, Vuex, Vue Router, Nuxt.js, Bulma, Sass, HTML5, socket.io, Websockets, REST API, JSON, Python, Flask, Docker, Kubernetes, Google Cloud, Zeit/Vercel\smallskip
		\item [Tools:] Slack, JIRA, Confluence, GitHub, GitHub Actions, IntelliJ, Abstract, Storybook, Cypress, Jest, Sentry\smallskip
		\item [Methodologies:] Iterative Development, Agile (SCRUM, Kanban), Component-based Development, DevOps, Continuous Integration \& Deployment
	\end{description}

	\bigskip\bigskip

	\cvevent{Full-Stack Software Engineer}{\href{https://www.ubs.com/ch/en.html}{UBS}}{Jul 2017 -- Apr 2019}{Zurich}

	\bigskip
	\begin{itemize}[label=\color{bullet}\textbullet]
		\item Lead Frontend Engineer, oversaw web application development and architecture.
		\item Worked closely with UI/UX Designers and clients; conducted design workshops and product demos. Mentored Junior Software Engineers.
		\item Designed, built, and maintained Cloud infrastructure (Amazon Web Services, AWS). Orchestrated containerized applications in a microservices fashion.
		\item Setup Continuous Integration and Continuous Deployment pipelines as well as monitoring and alerting to enable a DevOps approach.
		\item Advised, coached, and presented tech talks to business and IT stakeholders regarding Cloud adoption and Cloud-first development.
	\end{itemize}

	\bigskip
	\begin{description}
	\small
		\item [Technologies:] Typescript, Javascript (ES6), Angular (4+), NgRx (Redux), RxJS, Bootstrap, Karma, Jasmine, AWS, Terraform, Docker, REST API, JSON, gRPC, Java 8 EE, Spring, Spring Boot, Redis\smallskip
		\item [Tools:] JIRA, Confluence, Bitbucket, Bitbucket Pipelines, Git, WebStorm, IntelliJ, InVision\smallskip
		\item [Methodologies:] Iterative Prototyping, Design Thinking, Agile (SCRUM), Functional Programming, Microservice Architecture, Infrastructure as Code, DevOps, Continuous Integration \& Deployment
	\end{description}

	\bigskip\bigskip

	\cvevent{Full-Stack Software Engineer}{\href{https://www.mimacom.com/}{mimacom}}{Oct 2016 -- Jun 2017}{Zurich \& Berne}

	\bigskip
	\begin{itemize}[label=\color{bullet}\textbullet]
		\item On-site technical consulting for Software Engineering projects, specialized in Frontend Development.
		\item Full-Stack development of prototypes and tools. In-house and on-site at the client.
		\item Provided development capacity and bug fixes for projects nearing deadline or with tight resources.
	\end{itemize}

	\bigskip
	\textbf{\small{Selected Projects}}:
	\smallskip
	\begin{itemize}[label=\color{bullet}\textbullet]
		\small
		\item \href{https://www.ebill.ch/}{eBill}, previously E-Rechnung for \href{https://www.six-group.com/en/site/banking-services/paynet.html}{SIX Paynet} \& Postfinance.
		\item Web component development using Avaloq Front Platform (\href{https://developer.avaloq.com/web/developer-portal/learn}{Banklet™}) for \href{https://www.avaloq.com/en/}{Avaloq}.
		\item \enquote{\href{https://blog.alertswiss.ch/de/rubriken/bevoelkerungsschutz/koordinierter-sanitaetsdienst-ksd-neues-management-tool-blue-screen-switzerland/}{KSD Bluescreen}}, web application for the coordination of primary medical care in emergency/crises for the Swiss Army (\href{https://www.vtg.admin.ch/de/organisation/astab/san/ksd.html}{Koordinierter Sanitätsdienst}).
	\end{itemize}

	\bigskip
	\begin{description}
		\small
		\item [Technologies:] Java 8 (EE), Spring, Spring Boot, Apache Maven, AngularJS, Angular (2+), Typescript, Javascript (ES6), Karma, Jasmine, Protractor, CucumberJS, REST API, JSON, SOAP, Oracle, MySQL, Elasticsearch\smallskip
		\item [Tools:] JIRA, Confluence, Bamboo/Bitbucket, Jenkins, IntelliJ, Git, BrowserStack\smallskip
		\item [Methodologies:] Agile (SCRUM), Behaviour Driven Development, Domain Driven Design, Service Oriented Architecture
	\end{description}

	\bigskip\bigskip

	\cvevent{Full-Stack Software Engineer}{\href{https://www.fides.ch}{Fides Treasury Services}}{Aug 2013 -- Oct 2016}{Zurich}

	\bigskip
	\begin{itemize}[label=\color{bullet}\textbullet]
		\item Lead Frontend Engineer and web expert on flagship products used by customers worldwide.
		\item Full-Stack development and maintenance of various applications used by large Swiss corporates for payment processing via SWIFT \& IBM MQ (including Sanction Screening).
		\item Implemented Continuous Integration and Continuous Deployment solutions and workflows. 
		\item 3rd level support of legacy applications.
	\end{itemize}

	\bigskip
	\begin{description}
	\small
		\item [Technologies:] Java 8 (EE), Spring, Spring Boot, JUnit, Mockito, Apache Maven, Apache Camel, IBM MQ, Javascript, AngularJS, jQuery, Bootstrap, Node.js, HTML5, CSS3, REST API, JSON, XML, ISO20022, SWIFT, MSSQL\smallskip
		\item [Tools] JIRA, Confluence, Jenkins, Sonatype Nexus, SonarSource, SVN, Tomcat, IntelliJ, Eclipse\smallskip
		\item [Methodologies] Extreme Programming, Agile (SCRUM), Waterfall, Test Driven Development, Service Oriented Architecture
	\end{description}

	\newpage

	\cvevent{Junior Software Engineer (Apprentice)}{\href{https://www.swisscard.ch/en/}{Swisscard AECS}}{Nov 2012 -- Aug 2013}{Zurich, Switzerland}

	\bigskip
	\begin{itemize}[label=\color{bullet}\textbullet]
		\item Intern as part of Credit Suisse Apprenticeship program.
		\item Developed web application for credit card risk scoring based on statistical models.
		\item Developed an application to correct discrepancies and inconsistencies of credit card and transaction data.
		\item Maintained and improved various backend applications and tools for credit card payment processing.
	\end{itemize}

	\bigskip
	\begin{description}
		\small
		\item [Technologies:] Java 7 (EE), Spring, JUnit, Aquillian, Apache Maven, JSF, jQuery, Ajax, Bootstrap, SOAP, XML \& XSLT, XSD
		\item [Tools:] JIRA, Jenkins, SVN, IBM WebSphere Application Server, Eclipse
		\item [Methodologies:] Extreme Programming, Test Driven Development, Service Oriented Architecture
	\end{description}

	\bigskip\bigskip

	\cvevent{Junior Software Engineer (Apprentice)}{\href{https://www.credit-suisse.com/ch/en.html}{Credit Suisse}}{Aug 2009 -- Nov 2012}{Zurich, Switzerland}

	\bigskip
	\begin{itemize}[label=\color{bullet}\textbullet]
		\item Developed software modules and applications for error handling, tracing, and reporting for IBM z/OS mainframe systems used in end-of-day processing.
		\item Maintained and continued development on a web application used to test an extensive CORBA mainframe service.
		\item Migrated applications from Java 6 to Java 7.
	\end{itemize}

	\bigskip
	\begin{description}
		\small
		\item [Technologies:] Java 6 (EE), Java 7 (EE), JSF, Struts, CORBA, PL/1, IBM z/OS, IBM DB2, IBM IMS, JCL
		\item [Tools:] MS Project, TN3270 Terminal, Eclipse
	\end{description}
		
	\switchcolumn
	
	% ---------------------------------------
	% Education
	% ---------------------------------------
	\cvsection{Education}
	\cveventbreak{BSc Computer Science}{\href{https://www.ffhs.ch/}{Fernfachhochschule Schweiz (FFHS)}}{Sept 2017 -- present}{}

	\bigskip
	\cveventbreak{Berufsmatura}{\href{https://www.bzz.ch/}{Bildungszentrum Zürichsee (BZZ)}}{Aug 2009 -- Aug 2013}{}

	\bigskip
	\cveventbreak{Informatiker EFZ \\\small{Software Development}}{\href{https://www.bzz.ch/}{Bildungszentrum Zürichsee (BZZ)}}{Aug 2009 -- Aug 2013}{}

	% ---------------------------------------
	% Profile
	% ---------------------------------------
	\cvsection{Strengths}
	\cvstrength{Truly Full-Stack}{I understand the full stack -- from complex web applications to backend services to containers to infrastructure on the cloud.}

	\bigskip
	\cvstrength{Doer}{I enjoy getting my hands dirty and am always up to a challenge.}

	\bigskip
	\cvstrength{Quick Learner}{I can quickly learn and adapt to new domains and foreign technology.}
	
	\bigskip
	\cvstrength{Eye for Details}{I enjoy taking care of the small details to deliver a fantastic customer experience from start to finish.}

	\newpage
	
	% ---------------------------------------
	% Certifications
	% ---------------------------------------
	\cvsection{Certifications}
	% Date: January 2019
	\cveventbreak{\href{https://www.ireb.org/en/cpre/foundation/}{Certified Professional for Requirements Engineering}}{\href{https://www.ireb.org/en}{International Requirements Engineering Board (IREB)}}{}{}

	% Date: April 2017
	\bigskip
	\cveventbreak{\href{https://www.elastic.co/training/elasticsearch-engineer-1}{Elasticsearch Engineer I}}{\href{https://elastic.co}{elastic}}{}{}

	% Date: January 2011
	\bigskip
	\cveventbreak{\href{https://cyp.ch/smart-education/bankfit}{BankFIT: Banking and Financial Education for IT}}{\href{https://cyp.ch}{Center for Young Professionals in Banking (CYP)}}{}{}

	% ---------------------------------------
	% Projects
	% ---------------------------------------
	\cvsection{Personal Projects}
	
	\cveventbreak{\href{https://www.nome.io}{nome.io}}{Co-Founder \& CTO}{}{}
	\begin{itemize}[label=\color{bullet}\textbullet]
		\item Startup focused on personal branding, social media, and online identity.
	\end{itemize}
	
	\bigskip
	
	% https://web.archive.org/web/20111127060913/http://www.macstories.net/iphone/stage-review
	\cveventbreak{Stage}{Software Engineer \& Designer}{October 2009 -- January 2011}{}
	\begin{itemize}[label=\color{bullet}\textbullet]
		\item iOS application that allowed users to share music with their social media networks (Twitter, Facebook).
		\item Reached top 10 paid apps on the Swiss App Store within the first three days.
	\end{itemize}

	\bigskip
	
	% http://web.archive.org/web/*/www.iphone360.ch
	\cveventbreak{iPhone360}{Editor in Chief}{August 2008 -- February 2011}{}
	\begin{itemize}[label=\color{bullet}\textbullet]
		\item Weblog about Apple ecosystem and iOS apps.
		\item 1.9 mio total page views, 1000 daily visitors.
	\end{itemize}

	\newpage
	
	% ---------------------------------------
	% Volunteering
	% ---------------------------------------
	\cvsection{Volunteering}
	\cveventbreak{Supervisor of Apprentices \\\small{Berufsbildner}}{Fides Treasury Services}{Jul 2016 -- Oct 2016}{}

	% Lehrlingsbetreuer
	\bigskip
	\cveventbreak{Coaching of Apprentices\\\small{Betreuung der Lernenden}}{Fides Treasury Services}{Oct 2014 -- Jul 2016}{}

	\bigskip
	\cveventbreak{Medical Safety Officer \& First Aid Responder}{Fides Treasury Services}{Mar 2015 -- Oct 2016}{}

	% ---------------------------------------
	% Languages
	% ---------------------------------------
	\cvsection{Languages}
	\cvskill{German}{5}
	\cvskill{English}{4}
	\cvskill{French}{2}
	
	% ---------------------------------------
	% Interests
	% ---------------------------------------
	\cvsection{Interests}
	\begin{itemize}[label=\color{bullet}\textbullet]
		\item Photography
		\item Traveling
		\item Cooking
		\item Video Games
		\item Technology
	\end{itemize}

	% ---------------------------------------
	% References
	% ---------------------------------------
	\cvsection{References}
	On request.
	

\end{paracol}

\thispagestyle{last-page}
\end{document}

