\cvevent{Full-Stack Software Engineer}{\href{https://www.ubs.com/ch/en.html}{UBS}}{Jul 2017 -- Apr 2019}{Zurich, Switzerland}

\medskip
\begin{itemize}
	\item Lead Frontend Engineer, oversaw web application development and architecture, ranging from first prototype to production-ready using state of the art web technologies.
	\item Worked closely with UI/UX designers and clients; conducted design workshops and product demos.
	\item Designed, built and maintained Cloud infrastructure (Amazon Web Services, AWS); running containerized applications in a microservices fashion.
	\item Setup Continuous Integration and Continuous Deployment pipelines as well as monitoring and alerting to enable DevOps approach.
	\item Mentored Junior Frontend Engineers.
	\item Advised, coached and presented tech talks to business and IT stakeholders regarding Cloud adoption and Cloud-first development.
	\item Conducted first as well as technical interviews for candidates, screened applications.
\end{itemize}

\medskip
\begin{description}
	\ifincludestech
	\item [Technologies] Typescript, Javascript, Angular, NgRx (Redux), RxJS, Bootstrap, Karma, Jasmine, AWS, Terraform, Docker, REST API, JSON, gRPC, Java 8 EE, Spring, Spring Boot, Redis
	\fi
	\ifincludestools
	\item [Tools] JIRA, Confluence, Bitbucket, Bitbucket Pipelines, WebStorm, IntelliJ, Git, InVision
	\fi
	\ifincludesmethods
	\item [Methodologies] Iterative Prototyping, Design Thinking, Agile (SCRUM), Functional Programming, Microservice Architecture, Infrastructure as Code, DevOps
	\fi
\end{description}

\divider

\cvevent{Full-Stack Software Engineer}{\href{https://www.mimacom.com/}{mimacom}}{Oct 2016 -- Jun 2017}{Zurich \& Berne, Switzerland}

\medskip
\begin{itemize}
	\item On-site technical consulting for Software Engineering projects, specialised in Frontend Development.
	\item Full-Stack development of prototypes and tools, inhouse and for clients.
	\item Provided development capacity and bug fixes for projects nearing deadline or with tight resources.
\end{itemize}

\smallskip
\textbf{Selected Projects}:
\smallskip
\begin{itemize}
	\item \href{https://www.ebill.ch/}{eBill}, previously E-Rechnung for \href{https://www.six-group.com/en/site/banking-services/paynet.html}{SIX Paynet} \& Postfinance.
	\item Web component development using Avaloq Front Platform (\href{https://developer.avaloq.com/web/developer-portal/learn}{Banklet™}) for \href{https://www.avaloq.com/en/}{Avaloq}.
	\item \enquote{\href{https://blog.alertswiss.ch/de/rubriken/bevoelkerungsschutz/koordinierter-sanitaetsdienst-ksd-neues-management-tool-blue-screen-switzerland/}{KSD Bluescreen}}, web application for coordination of basic medical care in emergency/crisis situations for the Swiss Army (\href{https://www.vtg.admin.ch/de/organisation/astab/san/ksd.html}{Koordinierter Sanitätsdienst}).
\end{itemize}

\medskip
\begin{description}
	\ifincludestech
	\item [Technologies] Java 8 (EE), Spring, Spring Boot, Apache Maven, AngularJS, Angular, Typescript, Javascript, Karma, Jasmine, Protractor, CucumberJS, REST API, JSON, SOAP, XML \& XSLT, ISO20022, Oracle, MySQL, Elasticsearch
	\fi
	\ifincludestools
	\item [Tools] JIRA, Confluence, Bamboo, Jenkins, IntelliJ, Git, BrowserStack
	\fi
	\ifincludesmethods
	\item [Methodologies] Agile (SCRUM), Behaviour Driven Development, Domain Driven Design, Service Oriented Architecture
	\fi
\end{description}

\divider

\cvevent{Full-Stack Software Engineer}{\href{https://www.fides.ch}{Fides Treasury Services}}{Aug 2013 -- Oct 2016}{Zurich, Switzerland}

\medskip
\begin{itemize}
	\item Lead Frontend Engineer and web expert on flagship products used by customers worldwide.
	\item Full-Stack development and maintenance of various applications used by large Swiss corporates for payment processing via SWIFT \& IBM MQ (including Sanction Screening).
	\item Implemented Continuous Integration and Continuous Deployment solutions and workflows. 
	\item Conducted technical interviews for full-time positions as well as contracts; screened applications.
	\item 3rd level support of legacy applications.
\end{itemize}

\medskip
\begin{description}
	\ifincludestech
	\item [Technologies] Java 8 (EE), Spring, Spring Boot, JUnit, Mockito, Apache Maven, Apache Camel, IBM MQ, Javascript, AngularJS, jQuery, Bootstrap, Node.js, HTML5, CSS3, REST API, JSON, XML, ISO20022, MSSQL
	\fi
	\ifincludestools
	\item [Tools] JIRA, Confluence, Jenkins, Sonatype Nexus, SonarSource, SVN, Tomcat, IntelliJ, Eclipse
	\fi
	\ifincludesmethods
	\item [Methodologies] Extreme Programming, Agile (SCRUM), Waterfall, Test Driven Development, Service Oriented Architecture
	\fi
\end{description}

\divider

\cvevent{Junior Software Engineer}{\href{https://www.swisscard.ch/en/}{Swisscard AECS}}{Nov 2012 -- Aug 2013}{Zurich, Switzerland}

\medskip
\begin{itemize}
	\item Developed web application for credit card risk scoring based on statistical models.
	\item Developed an application to correct discrepancies and inconsistencies of credit card and transaction data.
	\item Maintained and improved various backend applications and tools for credit card payment processing.
\end{itemize}

\medskip
\begin{description}
	\ifincludestech
	\item [Technologies] Java 7 (EE), Spring, JUnit, Aquillian, Apache Maven, JSF, jQuery, Ajax, Bootstrap, SOAP, XML \& XSLT, XSD
	\fi
	\ifincludestools
	\item [Tools] JIRA, Jenkins, SVN, IBM Websphere Application Server, Eclipse
	\fi
	\ifincludesmethods
	\item [Methodologies] Extreme Programming, Test Driven Development, Service Oriented Architecture
	\fi
\end{description}

\divider

\cvevent{Junior Software Engineer}{\href{https://www.credit-suisse.com/ch/en.html}{Credit Suisse}}{Aug 2009 -- Aug 2013}{Zurich, Switzerland}

\medskip
\begin{itemize}
	\item Developed software modules and applications for error handling, tracing and reporting for IBM z/OS mainframe systems used in end-of-day processing.
	\item Maintained and continued development on a web application used to test an extensive CORBA mainframe service.
	\item Migrated applications from Java 6 to Java 7.
\end{itemize}

\medskip
\begin{description}
	\ifincludestech
	\item [Technologies] Java 6 (EE), Java 7 (EE), JSF, Struts, CORBA, PL/1, IBM z/OS, IBM DB2, IBM IMS, JCL
	\fi
	\ifincludestools
	\item [Tools] MS Project, TN3270 Terminal, Eclipse
	\fi
\end{description}
